---
title: "Lab 4: **Rmarkdown**, package **dplyr**, package **stargazer**, and regression plots"
author: "Ngoc Phan"
date: "September 28, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, messages = F, warning = F, eval = FALSE)
```

# Intro to RMarkdown
- Create Markdown Document
- Knit to HTML/PDF/Word
- Headers
- **Bold**
- _Italic_
- Bullet points
- [Embedded link](https://www.markdowntutorial.com/)
- R code chunks: Labels, options

# Manipulating/cleaning data with **dplyr**

As I showed you in the last lab, cleaning data with base R can be tricky and confusing. However, the beauty of R is that you can import packages that make these tasks much more straightforward.

```{r Import data}
library(readstata13)
happy <- read.dta13("happy_planet.dta")
colnames(happy)
```

```{r Install and Open package dplyr}
#install.packages("dplyr")
library(dplyr)
```


In the following subsections, we are going to contrast how we do certain tasks in base R and the way we do it in **dplyr**.

## _Select_: Keeping and dropping variables

```{r Keep and drop variables}
#Base R
happy1 <- happy[, c("country", "lifesat010", "hdi", "gdppercapitappp")]
colnames(happy1)

#Dplyr
happy2 <- select(happy, country, lifesat010, hdi)
happy2 <- select(happy, country:population)

#Drop variables
happy3 <- select(happy, -region)
```


## _Filter_: Returning rows with matching conditions

```{r Return rows with matching conditions}

#Base R
happy4 <- happy[happy$Africa == 1, ]


#Dplyr
happy4 <- filter(happy, Africa == 1)
happy5 <- filter(happy, population > 5)

```

## Dropping missing values

```{r Drop missing values}
#summary(happy)
#is.na(happy$hdi)

#filter(happy, is.na(hdi))
#filter(happy, !is.na(hdi))

happy <- filter(happy, !is.na(hdi))
```

## _Arrange_: Sorting data

```{r Sort data}

#Create a dataset of Western countries, keeping only four variables
west <- filter(happy, West == 1)
west <- select(west, country, lifesat010, hdi, population)

#Base R
#order(west$lifesat010)

west1 <- west[order(west$lifesat010), ]

#head(west)
west2 <- west[c(6, 4, 2) , ]
#west2

#Dplyr
#arrange(west, lifesat010)
#arrange(west, -lifesat010)
#arrange(west, desc(lifesat010))

#arrange(west, hdi, population)
```

## _Mutate_: Creating new variables

```{r Create new variables}

#Base R
west$pop <- west$population*1000000
#west

#Dplyr
west <- select(west, -pop)
west <- mutate(west, pop = population*1000000)
```


# Nice regression output with Stargazer
```{r Model 1}
m1 <- lm(lifesat010 ~ hdi + lifeexpyears, data = happy)
summary(m1)

```


```{r Model 1 with Stargazer, results='asis', warning = F, message = F}
#install.packages("stargazer")
library(stargazer)
stargazer(m1, title = "Regression of Life Statisfaction on HDI")
```

```{r Stargazer with labels, results='asis'}
stargazer(m1, title = "Regression of Life Statisfaction on HDI",
          dep.var.labels = "Life Satisfaction",
          covariate.labels = c("Human Development Index", "GDP per capita PPP"))
```

# Plot regression line

```{r Model 2: Bivariate}
m2 <- lm(lifesat010 ~ hdi, data = happy)
plot(happy$hdi, happy$lifesat010, main = "Regression Line",
     xlab = "HDI", ylab = "Life Satisfaction")
abline(m2)
```

```{r Model 1: Multivariate}

#?abline
#m1$coefficients

plot(happy$hdi, happy$lifesat010, main = "Regression Line",
     xlab = "HDI", ylab = "Life Satisfaction")
abline(m1$coefficients["(Intercept)"], m1$coefficients["hdi"])

```

# Plot coefficients and confidence intervals
```{r Model 3}
happy <- mutate(happy, hdi100 = hdi*100)
m3 <- lm(lifesat010 ~ hdi100 + gdppercapitappp + lifeexpyears, data = happy)
summary(m3)
```

```{r Basic coefplots}
#install.packages("arm")
library(arm)
coefplot(m3)
```

```{r Coefplots with labels}
coefplot(m3, main = "Impact on Life Satisfaction",
         varnames = c("Intercept", "HDI", "GDP per capita PPP", "Life Expectancy"))
```

```{r Coefplots of selected variables: Failed version}
#summary(m3)$coefficients[, 1]
#summary(m3)$coefficients[, 2]
#summary(m3)$coefficients

coefplot(summary(m3)$coefficients[, 1],
         summary(m3)$coefficients[, 2],
         main = "Impact on Life Satisfaction")
```

```{r Coefplots of selected variables: }
coefplot(summary(m3)$coefficients[c("hdi100", "gdppercapitappp"), 1],
         summary(m3)$coefficients[c("hdi100", "gdppercapitappp"), 2], 
         varnames = c("HDI", "GDP per capita PPP"),
         main = "Impact on Life Satisfaction")
```

